A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-09-03 rr-flow.Rmd
remove make on windows section
break line so it fits on page
fix make docker relationship

Even when you have obtained a version of the project, and you can ensure that this version is unchanged, you may not know how to reproduce the results, because it is unclear what has to be run in which order. This job gets comfortable with `make`, since it allows you to create (computational) recipes too (re-)create files. A downside of `make` is, that the installation on Windows is not straightforward. However, if `docker` (see later sections) is available this is not an issue, since `make` ships with (almost) every `docker` image.

@@

Since `docker`'s commands grow long and are tedius to type, we advocate to use some automatic way to generate them. Unfortunatly is the most comfortable way only availible on linux, which uses `make DOCKER=TRUE` together with a Makefile like the one used for that article.

@@

build: Dockerfile
	sudo docker build -t $(projekt) .

clean:
	Ruby/clean.rb
	rm -rf kitematic
.PHONY: clean

>>>>

Even when you have obtained a version of the project, and you can ensure that this version is unchanged, you may not know how to reproduce the results, because it is unclear what has to be run in which order. This job gets comfortable with `make`, since it allows you to create (computational) recipes too (re-)create files.

@@

Since `docker`'s commands grow long and are tedius to type, we advocate to use some automatic way to generate them. Fortunatly one can use `make` to automaticly generate the `docker` commands, e.g. the (simplified) Makefile for this paper allows command after `$(run)` to be condtionally passed through docker if one calls `make DOCKER=TRUE`:

@@

build: Dockerfile
	docker build -t $(projekt) .
